On the Synchronization of Computational RFIDs

### 2018-07-01 TMC-2017-11-0695.R1-main.tex
add Amjad biography

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Henko Aantjes}
Biography text here.
\end{IEEEbiographynophoto}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/przemek.jpg}}]{}
Biography text here.	
\end{IEEEbiography}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/amjad.jpg}}]{Amjad Yousef Majid}
Biography text here.
\end{IEEEbiography}
%
% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

>>>>

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Henko Aantjes}
Biography text here.
\end{IEEEbiographynophoto}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/przemek.jpg}}]{}
Biography text here.	
\end{IEEEbiography}
%
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{author_photos/amjad.jpg}}]{Amjad Yousef Majid}
obtained his MSc. in Computer science from Delft University of Technology in 2015. Currently, he is a PhD. candidate at Embedded Software Group at Delft University. His research focuses on intermittent software architecture, (computational) RFID systems, backscatter technology, and wireless sensor networks.  
\end{IEEEbiography}
%
% insert where needed to balance the two columns on the last page with
% biographies
%\newpage
